Reflections from reproductions

### 2024-12-10 pages/reflections.qmd
feat(images): making eval_charts (a) save to png, (b) colourblind friendly, (c) percentage overlaid
docs(quarto): address TODO and tweak 94% to 94.1%
docs(reflections): reorganised to match order and categories in article

<!-- TODO: Once complete, carefully go over again and check everything is correct -->

This page describes the facilitators for each reproduction (and, conversely, the barriers to the reproduction, in their absence). With each section, I have created a table which evaluates whether the facilitators were fully met (✅), partially met (🟡), not met (❌) or not applicable (N/A) for each study.

@@

eval_chart(criteria_wide)
```

## Environment

@@

## List required packages

@@

## Provide versions

@@

## Structure of code and scripts

@@

## Model is provided in a "runnable" format

@@

@@

## Don't hard code parameters that you will want to change for scenario analyses

@@

## Avoid large amounts of code duplication

## Include sufficient comments in the code

## Run time and memory usage

## Quicker models are easier to work with

I have not evaluated like as a criteria, as a long run time is not inherently a bad thing. However, I definitely found that the run time of models had a big impact on how easy it was to reproduce results as longer run times meant it was tricky (or even impossible) to run in the first place, or tricky to re-run.

The studies where I made adjustments were:

## For slow models, state the expected run time

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ❌ | ❌ | N/A | ✅ | 🟡 | 🟡 |

@anagnostou_facs-charm_2022: Not applicable. Very quick! Seconds! So not particularly relevant - although, you could argue, potentially still important if there were some error that made it look like the model were running continuously (e.g. stuck in a loop) - although this is relatively unlikely.

## For computationally expensive models, state memory usage and provide alternatives for lower spec machines

As I felt this was relatively subjective, as depending on what I felt to be "computationally expensive", as I didn't record the memory usage of all models, it felt unfair to do this as a checklist, and so have just informally noted below:

* @shoaib_simulation_2021, @huang_optimizing_2019, and @lim_staff_2020: Not applicable. Didn't find it to be too computationally expensive for my machine.
* @kim_modelling_2021: Unable to run on my machine (`serial` took too long to run (would have to leave laptop on for many many hours which isn't feasible), and `parallel` was too computationally expensive and crashed the machine (with the original number of people)). This is not mentioned in the repository or paper, but only referred to in a prior publication. Would've been handy if it included suggestions like reducing number of people and so on (which is what I had to do to feasibly run it).
* @anagnostou_facs-charm_2022: Not applicable. Runs in seconds.
* @johnson_cost_2021: It becomes more computationally expensive if try to run lots at once in simultaneous terminals. Didn't try running one on local machine with full parameter due to long run time making it infeasible, but knowing my system specs, it should have been able to if did.
* @hernandez_optimal_2015: This had long run times but I don't know if it was computationally expensive or not - I just know that I didn't run into any issues (but I didn't record memory usage, so its possible a lower-specced machine might).
* @wood_value_2021: Not applicable. As stated in their prior paper, the model is constrained by processing time, not computer memory.

## Parameters, scenarios and outputs

## Provide code for all scenarios

## All the required outputs are calculated/provided

## Include correct parameters in the script (even if just for one scenario)

@@

## Output format

## Understandable output tables

## Avoid large file sizes if possible

## Seeds

## Use seeds to control stochasticity

## Code to produce article results

This is a common problem across all item types, and a key part of STARS 2.0 for reproducibility.

## Provide code to process results into tables

## Provide code to process results into figures

## Provide code to calculate in-text results

## Documentation

## Include instructions on how to run the model/script

## Other

@@

**Excessive number of files**. For @hernandez_optimal_2015 the default behaviour of the script was to output lots of files from each round (so you could easily have 90, 100, 200+ files), which were then not used in analysis (as it just depended on an aggregate results file). Although these individual files might be useful during quality control, as a default behaviour of the script, it could easily make the repository quite busy/littered with files.

@@

**Version history and releases**. @johnson_cost_2021 had commits to their GitHub repository after the publication date. It wasn't clear which version aligned with the publication. However, the most recent commits add clear README instructions to the repository. We decided to use the latest version of the repository, but it would have beneficial to have releases/versions/a change log that would help to outline the commit history in relation to the publication and any subsequent changes.

>>>>

This page describes the facilitators and barriers encountered in each reproduction, presented as a series of recommendations. These are grouped into two themes:

* Recommendations to support reproduction
* Recommendations to facilitate troubleshooting

With each section, I have created a table which evaluates whether the facilitators were fully met (✅), partially met (🟡), not met (❌) or not applicable (N/A) for each study.

@@

eval_chart(criteria_wide).show(config={'displayModeBar': False})
```

## Recommendations to support reproduction.

### Set-up

@@

## Share code with an open licence

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ❌ | ✅ | ✅ | ✅ | ❌ | ❌ |

Absence of licence prevents legal reuse of code for reproduction.

## Link publication to a specific version of the code

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| | | | | | ❌ | | |

<!--TODO: Check if any other studies had commits after publication-->

@johnson_cost_2021: Not met. Had commits to their GitHub repository after the publication date. It wasn't clear which version aligned with the publication. However, the most recent commits add clear README instructions to the repository. We decided to use the latest version of the repository, but it would have beneficial to have releases/versions/a change log that would help to outline the commit history in relation to the publication and any subsequent changes.

## List required packages and versions

### Packages and versions

### Packages

@@

### Versions

@@

### Running the model

## Provide code for all scenarios and/or sensitivity analyses

## Ensure model parameters are correct

## Control randomness

### Outputs

## Include code to calculate all required model outputs

@@

## Include code to generate the tables, figures and other reported results

### Summary

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | ❌ | ❌ | 🟡 | 🟡 | ✅ |

### Provide code to process results into tables

### Provide code to process results into figures

### Provide code to calculate in-text results

## Recommendations to support troubleshooting and reuse

### Design

## Separate model code from applications

@@

## Avoid hard-coded parameters

Don't hard code parameters that you will want to change for scenario analyses

## Minimise code duplication

### Clarity

## Comment sufficiently

## Ensure clarity and consistency in the model results tables

## Include run instructions

## State run times and machine specifications

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| 🟡 | ❌ | 🟡 | ❌ | ❌ | 🟡 | 🟡 | 🟡 |

### State run time

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ❌ | ❌ | ❌ | ✅ | 🟡 | 🟡 |

@anagnostou_facs-charm_2022: Not met! Although it only took seconds, you could argue that stating this is still important if there were some error that made it look like the model were running continuously (e.g. stuck in a loop) - and as it helps someone identify that they are able to run it on their machine

### State machine specification

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ✅ | ❌ | ❌ | ❌ | ❌ | ❌ |

Regarding the one that did describe it:

* @lim_staff_2020: Describe in article ("desktop computer (Intel Core i5 3.5 GHz, 8 GB RAM)")

### Computationally expensive models

Regarding whether models were computationally expensive...

* @shoaib_simulation_2021, @huang_optimizing_2019, and @lim_staff_2020, @anagnostou_facs-charm_2022: No issues
* @kim_modelling_2021: Unable to run on my machine (`serial` took too long to run (would have to leave laptop on for many many hours which isn't feasible), and `parallel` was too computationally expensive and crashed the machine (with the original number of people)). This is not mentioned in the repository or paper, but only referred to in a prior publication. Would've been handy if it included suggestions like reducing number of people and so on (which is what I had to do to feasibly run it).
* @johnson_cost_2021: It becomes more computationally expensive if try to run lots at once in simultaneous terminals. Didn't try running one on local machine with full parameter due to long run time making it infeasible, but knowing my system specs, it should have been able to if did.
* @hernandez_optimal_2015: This had long run times but I don't know if it was computationally expensive or not - I just know that I didn't run into any issues (but I didn't record memory usage, so its possible a lower-specced machine might).
* @wood_value_2021: Not applicable. As stated in their prior paper, the model is constrained by processing time, not computer memory.

### Functionality

## Optimise model run time

The run time of models had a big impact on how easy it was to reproduce results as longer run times meant it was tricky (or even impossible) to run in the first place, or tricky to re-run. The studies where I made adjustments were:

## Avoid excessive output files

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| N/A | N/A | N/A | N/A | N/A | N/A | ❌ | N/A |

For @hernandez_optimal_2015 the default behaviour of the script was to output lots of files from each round (so you could easily have 90, 100, 200+ files), which were then not used in analysis (as it just depended on an aggregate results file). Although these individual files might be useful during quality control, as a default behaviour of the script, it could easily make the repository quite busy/littered with files.

## Address large file sizes

## Other recommendations

@@

@@

@@

@@

@@
